Bayesian Exploration in Deep Reinforcement Learning

### 2022-08-25 papers/CDRL/sample_paper.tex
Update paper
final QQFLOW
TEMPORARY DEPLOY COMMIT

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

We propose to use conditional normalizing flows to model the value distribution,
\(Z^\pi\), with a continous estimate. As opposed to quantile previous work on 
quantile regression methods, which aim to minimize the Wasserstein distance
to the target distribution, normalizing flows minimize KL-divergence. Our target
is thus the KL-divergence from the target to the value distribution
\footnote{Check order later}.

\begin{equation}
  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{\hat{\T}
  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}
\end{equation}

Using conditional normalizing flows described in Section~\ref{sec:cnf}, we
define the value distribution model as an elementwise transformation of a
standard normal distribution conditioned on a low-dimensional representation of
the state \(\rvx\).

\begin{equation}
  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
\end{equation}
\begin{equation*}
  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
\end{equation*}

>>>>

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
\usepackage{minted}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

We propose to use conditional normalizing flows to model the value distribution,
\(Z^\pi\), with a continous estimate. As opposed to previous work on 
quantile regression methods, which aim to minimize the Wasserstein distance
to the target distribution, normalizing flows minimize the KL-divergence. Our
target is thus the KL-divergence from the value to the target distribution.

\begin{equation}
  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{Z_{\theta}(\rvx,a)}{\hat{\T}
  Z_{\tilde{\theta}}(\rvx,a)}
\end{equation}

Using conditional normalizing flows described in Section~\ref{sec:cnf}, we
define the value distribution model as a transformation of a
standard normal distribution conditioned on the state \(\rvx\).

% Similar to other DQN methods, we let \(Z_\theta(\rvx, a)\) be the \(a\)-th
% element of a function \(\tilde{Z}_\theta : \R^{\lvert \X \rvert}
% \rightarrow \R^{\lvert \A \rvert}\). This means that we need a conditional
% normalizing flow \(v_\theta : \R^{\lvert \X \rvert} \times \R^{\lvert \A \rvert}
% \rightarrow \R^{\lvert \A \rvert}\). Given that we have

Starting with a random variable \(S\) with a standard normal distribution
\(\N(0, I_{\lvert \A \rvert})\), we want a function \(v_\theta = v_{\theta_K}
\circ \dots \circ v_{\theta_2} \circ v_{\theta_1} \), such that
\(Z_\theta(\rvx, a) = v_\theta(S; \rvx)_a\). To learn \(v_\theta\) we note that
we can take the inverse transformation \(v^{-1}_\theta\) of the value
distribution to recover a random variable with the standard normal distribution,
i.e. \(S = v^{-1}_\theta(Z_\theta; \rvx)\). This further means that

\begin{equation}
  S^\prime \eqdist v^{-1}_\theta \left(\T v_\theta(S; \rvx); \rvx^\prime \right).
\end{equation}

We can use this

\begin{minted}[mathescape,
  linenos,
  numbersep=5pt,
  gobble=2,
  frame=lines,
  framesep=2mm]{csharp}
string title = "This is a Unicode π in the sky"
/*
Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
of an $n$-sided regular polygon circumscribing a
circle of diameter $d$.
*/
const double pi = 3.1415926535
\end{minted}

% \begin{equation}
%   \T \tilde{Z}_\theta(\rvx)_a \defeq R(\rvx, a) + \max_{a^\prime \in \A}
%   \tilde{Z}_\theta(\rvx^\prime)_{a^\prime}
% \end{equation}

% \noindent
% we can see that any learning signal would only come for a single action. This
% means that we need an elementwise flow so that we can learn each dimension
% independently. Given elementwise conditional normalizing flow \(v_\theta\), we
% define the loss function as

% \begin{multline}
%   \mathcal{L}_{\rvx, a}(\theta) \defeq \log p(v_\theta^{-1} (\rvx, v_{\tilde{
%   \theta}} (\rvx^\prime, \vepsilon))_a; 0, 1) \\- \log
%   \left\lvert \frac{\partial v^{-1}_{\theta}(\rvx, v_{\tilde{
%   \theta}} (\rvx^\prime, \vepsilon))_a}{\partial v_{\tilde{
%   \theta}} (\rvx^\prime, \vepsilon)_a} \right\rvert; \quad
%   \vepsilon \sim \N(0, I_{\lvert \A \rvert})
% \end{multline}

The most popular normalizing flows right now are buildt for large dimensional
spaces such as images. This includes coupling and autoregressive flows. Planar
flow is very easy to turn elementwise, but unfortunately does not have a closed
form inverse for most functions of \(h\). Although it does have one for
piecewise linear funcitons, those do not have second derivative, hence the
gradient of the log absolute determinant would be zero. This would mean it can
not learn appropriate transformations. Instead we define our own flow.

Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
flow, this function is invertible and differentiable given any values for these
parameters. Equation~\ref{eq:luddeflow_inv} and
Equation~\ref{eq:luddeflow_grad} show the closed form gradient.

% \begin{equation}
%   Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
% \end{equation}
% \begin{equation*}
%   z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
% \end{equation*}

% \begin{equation*}
%   s(x) = \log(1 + \exp(x))
% \end{equation*}
% \begin{equation}
%   v_{w, b, c, d}(z) = \sign(z + c) \left[ s(\lvert w(z + c) \rvert + b) 
%   - s(b) \right] + d \label{eq:luddeflow}
% \end{equation}

% \begin{equation*}
%   s^{-1}(x) = \log(\exp(x) - 1); \quad x > 0
% \end{equation*}
% \begin{equation}
%   v^{-1}_{w, b, c, d}(z^\prime) = \frac{\sign(z^\prime - d)}{w}
%   [ s^{-1}(\lvert z^\prime - d \rvert + s(b)) - b] - c \label{eq:luddeflow_inv}
% \end{equation}

% \begin{equation}
%   \frac{\partial v^{-1}_{w,b,c,d}}{\partial z^\prime} = \frac{(e^b + 1) 
%   e^{\lvert z^\prime - d \rvert}}{w (e^b + 1)e^{\lvert z^\prime - d \rvert} - w}
%   \label{eq:luddeflow_inv_grad}
% \end{equation}

\begin{equation}
  v(z; b, c, d) = \sign(z - c) \log \left( e^{\lvert x - c \rvert}
   + e^{b} - 1 \right) + d \label{eq:luddeflow}
\end{equation}

\begin{equation}
  \frac{\partial v(z; b, c, d)}{\partial z} = \frac{e^{\lvert x - c \rvert}}
  {e^{\lvert x - c \rvert} + e^{b} - 1}
  \label{eq:luddeflow_grad}
\end{equation}

\begin{equation}
  v^{-1}(z^\prime; b, c, d) = v(z^\prime; -b, d, c) \label{eq:luddeflow_inv}
\end{equation}

Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
description is \(w\) changes the slope of the function, \(b\) changes the
\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
vertically.

\begin{figure}[ht]
  \vspace{.3in}
  % \centerline{\fbox{This figure intentionally left non-blank}}
  \includegraphics[width=\columnwidth]{luddeflow.png}
  \vspace{.3in}
  \caption{Illustration of the effect the free parameters have on the function).
  }\label{fig:luddeflow}
\end{figure}
